formula1

### 2020-05-25 inst/formula1.Rmd
work on Zipf's law

>>>>

# Zipf's law

Do the players follow Zipf's law?

```{r,defzip}
zipf <- function(n){
	out <- 1/seq_len(n)
	out/sum(out)
}
zipf(9)
```

Then there are two natural ways to proceed:

```{r,cache=TRUE}
mf <- maxp(formula1)
l0 <- loglik(indep(mf),formula1)
l1 <- loglik(indep(zipf(size(formula1))),formula1)
c(l0,l1)
pchisq(2*(l0-l1),df=size(formula1)-1,lower.tail=FALSE)
```

However, this uses Zipf's law according to the players' points rating,
and it might be better to rank the players according to their
likelihood rating.

```{r}
mf
mf[rank(-mf)] <- zipf(size(formula1))
mf
l2 <- loglik(indep(mf),formula1)
l2
pchisq(2*(l0-l1),df=size(formula1)-1,lower.tail=FALSE)
```

which is even worse.
